Combining neural networks and geostatistics for landslide hazard assessment of San Salvador Metropolitan Area, El Salvador \newline \newline Combinando redes neuronales y geoestad\'{i}stica para evaluaci\'{o}n de deslizamientos de tierra de el \'{a}rea Metropolitana de San Salvador, El Salvador

### 2015-05-31 paper.tex
31 May 2015 9:50
31 May 2014 11:30

\pagestyle{fancy}
\fancyhead{}
\fancyhead[RE]{\thepage \hfill {\sc r. ríos -- c.gámez }}
\fancyhead[LO]{{\sc Combining neural networks and geostatistics for landslide hazard assessment of San Salvador Metropolitan Area, El Salvador } \hfill \thepage}
\fancyfoot{}
\fancyfoot[RE]{{\scriptsize{\it Rev.Mate.Teor.Aplic.} (ISSN 1409-2433) {Vol. 19}(1): 1--10, January 2012}}
\fancyfoot[LO]{{\scriptsize{\it Rev.Mate.Teor.Aplic.} (ISSN 1409-2433) {Vol. 19}(1): 1--10, January 2012}}
\paginas{1}{10} % Numeros de página, la versión final la pone el editor; Page numbers, the Editor puts the final numbers
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphics}
\usepackage{graphicx} % En caso de usar figuras, con formato .esp; In case of using figures, with format .eps
\usepackage{float} 
\usepackage{url}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{enumerate}
\usepackage{authblk}

@@

\selectlanguage{spanish}
\begin{resumen}
Esta contribución describe como se obtuvo un modelo de evaluación de deslizamiento de tierra para San Salvador, departamento de El Salvador. El análisis inicio con la obtención de una foto área del SNET-MARN con un total de 939407 puntos georeferenciados con el fin de producir un inventario de deslizamiento. En esta evaluación de los deslizamientos se uso 4792 eventos previamente foto-interpretados y 7 factores condicionantes incluyendo: geomorfología, geología, precipitaciones máximas, aceleraciones sísmicas, pendiente del terreno, distancia a carretera y falla geológica. Redes Neuronales Artificiales(RNA) fueron usadas para la evaluación de la susceptibilidad a deslizamiento de tierra, logrando que más del 80\% de deslizamientos fueran apropiadamente clasificados usando un criterio dentro y fuera de la muestra con la que se estimaron los parámetros del modelo. Regresión Logística fue usada como base de comparación, obteniendo este modelo un rendimiento inferior que el de RNA con un porcentaje de correcta clasificación abajo del 70\%. Para completar el análisis se realizo la interpolación de puntos usando el método krigging proveniente del enfoque geoestadístico. Finalmente, los resultados muestran que es posible obtener un mapa de riesgo a deslizamiento de tierra, haciendo uso de una combinación de RNA y técnicas geoestadísticas con lo cual la presente investigación puede ayudar a la mitigación de deslizamientos de tierra en El Salvador.
\end{resumen}

\PC deslizamiento de tierra, evaluación de riesgo, San Salvador, El Salvador, RNA, geoestadística.

\begin{abstract}
This contribution describes how we obtained a landslide hazard
assessment model for San Salvador, department in El Salvador. The analysis started with an aerial photointerpretation from  SNET-MARN ((Servicio Nacional de Estudios Territoriales - Ministerio de Medio Ambiente y Recursos Naturales)  with a total amount of 939407 georeferenced points to produce a landslide inventory. In this
landslide assessment we have used 4792 events previously photo-interpretaded
and 7 conditioning factors including: geomorphology, geology, rainfall intensity, peak ground accelaration, slope angle, road and fault distance. Artificial
Neural Networks (ANNs) were applied for the assessment of susceptibility to
landslides, achieving more than 80\% of landslide were properly classified using
in-sample and out of sample criteria. Logistic regression was used as base of
comparison, obtaining this model a performance lower than ANNs with a percentage of correct classification under 70\%. To complete the analysis we have
performed interpolation of the points using kriging method from geostatistical
approach. Finally, the results show that is possible to derive a landslide hazard map, making use of a combination of ANNs and geostatistical techniques
wherewith the present study can help landslide mitigation in El Salvador.
\end{abstract}

\KW landslide, hazard assessment, San Salvador, El Salvador, ANN, geostatistics.

@@

\section{Landslide inventory and data sources of input variables}
\label{sec:landsinvet}
The Landslide inventory was developed from photographic analysis on the study area, using 
aerial photo from SNET-MARN which is presented in the Figure \ref{fig:img01}, where white areas represent regions of landslide occurrence which were processed using the software ILWIS.

@@

Once that the white areas were georeferenced, a percentage of 0.5\% of the total points georeferenced shows landslide ocurrence. In addition to the landslide information the following data sources of input variables was given by SNET-MARN: 
\begin{enumerate}
\item {\bf Geomorphology:} refers to landforms that result from lithospheric dynamics of geographic area.

\item {\bf Slope:} derived from digital elevation model MARN-SNET

@@

The method used for estimating the parameters of the model was an Hybrid Method: First of all Genetic Algorithms were used to avoid getting stuck in a local rather than a global minimum of error function, after that a local search was applied again to obtain a new local minimun.

@@

\section{Acknowledgment}   
The authors are indebted to M.SC. Giovanni Molina from SNET who provided the data and useful information about landslide modelling techniques.

@@

%\bibitem[Erm(2005)]{Ermini2005327}
\bibitem{Ermini2005327}
Artificial neural networks applied to landslide susceptibility assessment.
\newblock \emph{Geomorphology}, 66\penalty0 (1–4):\penalty0 327 -- 343, 2005.

@@

>>>>

\pagestyle{fancy}
\fancyhead{}
\fancyhead[RE]{\thepage \hfill {\sc a. rib\'{o} -- g. molina -- r. r\'{i}os  }}
\fancyhead[LO]{{\sc Combining neural networks and geostatistics for landslide hazard assessment of San Salvador Metropolitan Area, El Salvador } \hfill \thepage}
\fancyfoot{}
\fancyfoot[RE]{{\scriptsize{\it Rev.Mate.Teor.Aplic.} (ISSN 1409-2433) {Vol. 19}(1): 1--10, January 2012}}
\fancyfoot[LO]{{\scriptsize{\it Rev.Mate.Teor.Aplic.} (ISSN 1409-2433) {Vol. 19}(1): 1--10, January 2012}}
\paginas{1}{10} % Numeros de pgina, la versión final la pone el editor; Page numbers, the Editor puts the final numbers
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphics}
\usepackage{graphicx} % En caso de usar figuras, con formato .esp; In case of using figures, with format .eps
\usepackage{float} 
\usepackage{url}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{enumerate}
\usepackage{authblk}

@@

%\newpage

\selectlanguage{spanish}
\begin{resumen}
Esta contribución describe como se obtuvo un modelo de evaluación de deslizamiento de tierra para San Salvador, departamento de El Salvador. El análisis inicio con la obtención de una foto área del MARN () con un total de 939407 puntos georeferenciados con el fin de producir un inventario de deslizamiento. En esta evaluación de los deslizamientos se uso 4792 eventos previamente foto-interpretados y 7 factores condicionantes incluyendo: geomorfología, geología, precipitaciones máximas, aceleraciones sísmicas, pendiente del terreno, distancia a carretera y falla geológica. Redes Neuronales Artificiales(RNA) fueron usadas para la evaluación de la susceptibilidad a deslizamiento de tierra, logrando que más del 80\% de deslizamientos fueran apropiadamente clasificados usando un criterio dentro y fuera de la muestra con la que se estimaron los parámetros del modelo. Regresión Logística fue usada como base de comparación, obteniendo este modelo un rendimiento inferior que el de RNA con un porcentaje de correcta clasificación abajo del 70\%. Para completar el análisis se realizo la interpolación de puntos usando el método krigging proveniente del enfoque geoestadístico. Finalmente, los resultados muestran que es posible obtener un mapa de riesgo a deslizamiento de tierra, haciendo uso de una combinación de RNA y técnicas geoestadísticas con lo cual la presente investigación puede ayudar a la mitigación de deslizamientos de tierra en El Salvador.
\end{resumen}

\PC deslizamiento de tierra, evaluación de riesgo, El Salvador, RNA, geoestadística.

\begin{abstract}
This contribution describes how we obtained a landslide hazard
assessment model for San Salvador, department in El Salvador. The analysis started with an aerial photointerpretation from  MARN (Ministry of Environment and Natural Resources of El Salvador)  with a total amount of 939407 georeferenced points to produce a landslide inventory. In this
landslide assessment we have used 4792 events previously photo-interpretaded
and 7 conditioning factors including: geomorphology, geology, rainfall intensity, peak ground accelaration, slope angle, road and fault distance. Artificial
Neural Networks (ANNs) were applied for the assessment of susceptibility to
landslides, achieving more than 80\% of landslide were properly classified using
in-sample and out of sample criteria. Logistic regression was used as base of
comparison, obtaining this model a performance lower than ANNs with a percentage of correct classification under 70\%. To complete the analysis we have
performed interpolation of the points using kriging method from geostatistical
approach. Finally, the results show that is possible to derive a landslide hazard map, making use of a combination of ANNs and geostatistical techniques
wherewith the present study can help landslide mitigation in El Salvador.
\end{abstract}

\KW landslide, hazard assessment, El Salvador, ANN, geostatistics.

@@

\section{Landslide inventory and data sources of input variables}
\label{sec:landsinvet}
The Landslide inventory was developed from photographic analysis on the study area, using 
aerial photo from MARN which is presented in the Figure \ref{fig:img01}, where white areas represent regions of landslide occurrence which were processed using the software ILWIS.

@@

Once that the white areas were georeferenced, a percentage of 0.5\% of the total points georeferenced shows landslide ocurrence. In addition to the landslide information the following data sources of input variables was given by MARN: 
\begin{enumerate}
\item {\bf Geomorphology:} refers to landforms that result from lithospheric dynamics of geographic area.

\item {\bf Slope:} derived from digital elevation model MARN

@@

The method used for estimating the parameters of the model was an Hybrid Method (\cite{McNelis2005}): Firstly heuristic genetic algorithm using a package developed in the R statistical software specifically developed for this purpose, was used to obtain 
a good estimation of the parameters of the model.

The R package can be accessed from the following web address:

 were used to avoid getting stuck in a local rather than a global minimum of error function, after that a local search was applied on the previous  to obtain a new local minimun.

@@

\section{Acknowledgment}   
The authors are indebted to M.SC. Giovanni Molina from MARN who provided the data and useful information about landslide modelling techniques.

@@

%\bibitem[Erm(2005)]{Ermini2005327}
\bibitem{Ermini2005327}
Artificial neural networks applied to landslide susceptibility assessment.
\newblock \emph{Geomorphology}, 66\penalty0 (1–4):\penalty0 327 -- 343, 2005.
\newblock ISSN 0169-555X
%\newblock \doi{http://dx.doi.org/10.1016/j.geomorph.2004.09.025}.
\newblock URL \url{http://www.sciencedirect.com/science/article/pii/S0169555X04002272}.

@@

\bibitem{McNelis2005}
Paul D. McNelis
\newblock Estimation of a Network with Evolutionary Computation
\newblock \emph{Academic Press},
  (11):\penalty0 59-84, 2005.
\newblock ISBN 9780124859678,
%\newblock \doi{http://dx.doi.org/10.1016/B978-012485967-8.50003-8}.
\newblock URL
  \url{http://www.sciencedirect.com/science/article/pii/B9780124859678500038}.
